No sign of recovery

### 2018-05-22 Manuscript.Rmd
Grafik mit Abweichung von Zufalls-Aussterben und Zufalls-Einwandern.

# Average of functional traits
res[ 8, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$CH, surv$Visit, mean), 2)
tmp <- summary(lmer(CH ~ yr + (yr|aID_STAO), data = surv))$coefficients
res[ 8, "Temporal-Trend"] <- formatC(tmp["yr", "Estimate"], format = "f", digits = 3)
tmp <- anova(lmer(CH ~ yr + (yr|aID_STAO), data = surv), lmer(CH ~ 1 + (yr|aID_STAO), data = surv))[2, "Pr(>Chisq)"]
res[ 8, "P-value"] <- formatC(tmp, format = "f", digits = 3)

res[9, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$SLA, surv$Visit, mean), 2)
tmp <- summary(lme(SLA ~ yr, random = ~ yr|aID_STAO, data = surv))$tTable
res[9, "Temporal-Trend"] <- formatC(tmp["yr", "Value"], format = "f", digits = 3)
res[9, "P-value"] <- formatC(tmp["yr", "p-value"], format = "f", digits = 3)

res[10, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$SM, surv$Visit, mean), 2)
tmp <- summary(lme(SM ~ yr, random = ~ yr|aID_STAO, data = surv))$tTable
res[10, "Temporal-Trend"] <- formatC(tmp["yr", "Value"], format = "f", digits = 3)
res[10, "P-value"] <- formatC(tmp["yr", "p-value"], format = "f", digits = 3)

@@

The different measures of total community structure suggested that plant communities in mountain hay meadows were stable between 2003 and 2017 (Table \@ref(temporaltrends)): for each of the three 5-year survey periods the averages of alpha-, beta- and gamma-diversity, average Ellenberg values for temperature, nutrients, light and huminity, and average of species' canopy height, specific leaf area and seed mass did not vary much among the three sampling periods. For all measures, all p-values of the average temperal trends per site were $>0.05$ and only in the case of the average temperature value of the species the p-value was $<0.1$. Note that beta- and gamma-diversity are note available for single sites and thus mixed models to calculate the p-value could not be applied.

@@

@@

```{r}
# Calculate trend for all species
gettrend <- function(s) {
  tt <- surv %>% left_join(pl %>% filter(aID_SP == s) %>% dplyr::select(aID_KD, Occ)) %>% 
    replace_na(list(Occ = 0))
  trend <- NA
  try(trend <- glmer(Occ ~ yr + (1|aID_STAO), data = tt, family = binomial) %>% 
    tidy() %>% 
    filter(term == "yr") %>% 
    pull(estimate))
trend
}
res <- pl %>% group_by(aID_SP, T, F, N, L) %>% 
  summarise(Nsites = n_distinct(aID_STAO),
            Nrecords = n())
res$Trend <- map_dbl(res$aID_SP, gettrend)

# Is trend of species related to Ellenberg values
gls(Trend ~ N, data = res) %>% 
  tidy

library("nlme")
vf <- varExp(form=~Nrecords)
gls(Trend ~ T, data = res %>% filter(!is.na(T)), weights=vf) %>% summary
gls(Trend ~ F, data = res %>% filter(!is.na(F)), weights=vf) %>% summary
gls(Trend ~ N, data = res %>% filter(!is.na(N)), weights=vf) %>% summary
gls(Trend ~ L, data = res %>% filter(!is.na(L)), weights=vf) %>% summary

cor.test(res$T, res$N)
```

```{r}
# Borrowoing ideas from community assembly
library(geometry)

getFric <- function(x) {
  tt <- pl %>% 
  filter(!is.na(T) & !is.na(F) & !is.na(N) & !is.na(L)) %>% 
  filter(aID_KD == x) %>% dplyr::select(T, F, N, L) 
  geometry::convhulln(tt, "FA")$vol
}

surv$FRic <- map_dbl(surv$aID_KD, getFric)

summary(lmer(FRic ~ yr + (yr|aID_STAO), data = surv))
tapply(surv$FRic, surv$Visit, mean)

ex1 <- dbFD(dummy$trait, dummy$abun)
ex1
```

--> Es gibt keine Einheitlichen Entwicklungen der Communities. Das heisst aber nicht, dass es keine systematischen Veränderungen gibt!

```{r}
# Functions 
getsamples <- function(s, nspec, d, EL) {
  sample(d %>% pull(paste(EL)), nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

getsim <- function(x, EL, gain) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    summarise(Occ1 = sum(Visit == 1),
              Occ2 = sum(Visit == 2),
              Occ3 = sum(Visit == 3))
  if(gain)  ausw <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  if(!gain) ausw <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmp <- map_dbl(1:nsim, getsamples, nspec = sum(ausw), d = tt, EL = EL)
  list(
    nchange = sum(ausw),
    meanreal = mean(tt[ausw, paste(EL)] %>% unlist, na.rm = TRUE),
    mean = mean(tmp, na.rm = TRUE),
    lower = quantile(tmp, probs = 0.025, na.rm = TRUE),
    upper = quantile(tmp, probs = 0.975, na.rm = TRUE))
}

res <- sites %>% 
  filter(NTOT < 4) %>% 
  transmute(aID_STAO = aID_STAO, Sitemeasure = NTOT)
tmp <- map(res$aID_STAO, getsim, EL = "N", gain = TRUE)
res$meanreal <- tmp %>% map_dbl("meanreal")
res$mean <- tmp %>% map_dbl("mean")
res$lower <- tmp %>% map_dbl("lower")
res$upper <- tmp %>% map_dbl("upper")
ggplot(res, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black", alpha = 0.4) +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey", alpha = 0.4)

>>>>

@@

The different measures of total community structure suggested that plant communities in mountain hay meadows were stable between 2003 and 2017 (Table \@ref(temporaltrends)): for each of the three 5-year survey periods the averages of alpha-, beta- and gamma-diversity and the average Ellenberg values for temperature, nutrients, light and huminity did not vary much among the three sampling periods. For all measures, all p-values of the average temperal trends per site were $>0.05$ and only in the case of the average temperature value of the species the p-value was $<0.1$. Note that beta- and gamma-diversity are note available for single sites and thus mixed models to calculate the p-value could not be applied.

@@

```{r diffromrandom}
# Function to sample community and callculate CM
getsamples <- function(s, nspec, d, EL) {
  sample(d %>% pull(paste(EL)), nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

# Prepare data from one site and calculate mean and CrI for sample and mean for real community
getsim <- function(x, EL, gain) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    summarise(Occ1 = sum(Visit == 1),
              Occ2 = sum(Visit == 2),
              Occ3 = sum(Visit == 3))
  if(gain)  ausw <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  if(!gain) ausw <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmp <- map_dbl(1:nsim, getsamples, nspec = sum(ausw), d = tt, EL = EL)
  list(
    nchange = sum(ausw),
    meanreal = mean(tt[ausw, paste(EL)] %>% unlist, na.rm = TRUE),
    mean = mean(tmp, na.rm = TRUE),
    lower = quantile(tmp, probs = 0.025, na.rm = TRUE),
    upper = quantile(tmp, probs = 0.975, na.rm = TRUE))
}

# Function to prepare the res file for plotting
makesim <- function(EL, gain) {
  res <- sites %>% 
    filter(NTOT < 4) %>% 
    transmute(aID_STAO = aID_STAO, Sitemeasure = NTOT)
  tmp <- map(res$aID_STAO, getsim, EL = EL, gain = gain)
  res$meanreal <- tmp %>% map_dbl("meanreal")
  res$mean <- tmp %>% map_dbl("mean")
  res$lower <- tmp %>% map_dbl("lower")
  res$upper <- tmp %>% map_dbl("upper")
  res
}

# Make calculations and plot
tres <- makesim("N", gain = FALSE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNloss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(A) Species losses")

tres <- makesim("N", gain = TRUE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(B) Species gains")

multiplot(pNloss, pNgain, cols = 2)

@@
